### 2024-03-23 doc/sections/introduction.tex
Grow TODO list

\begin{enumerate}
      \item It makes sense to add a sequencing connective to MALL. This is
            motivated by coherence spaces (Retore), or by thinking in terms of
            session types.
      \item A sequent calculus is not possible (CITE: Tiu, Strassberger),
            but it is possible to define a proof calculus based on deep
            inference. (Also Retore's proof nets, but it turns out they define a
            different logic).
      \item To make sure that a proof system makes sense, we need some kind
            of Cut-elimination theorem that ensures that all proofs can be
            placed into a normal form where it is evident that it is not
            possible to derive all results.
\end{enumerate}

>>>>

\begin{itemize}
      \item BV by Guglielmi~\cite{Guglielmi07:sis} is an extension of MLL inspired by process algebras such as CCS~\cite{Milner89:CC,Milner80:CCS} and Pomset Logic~\cite{Retore97:pomset}.
      \item MAV by Hornes~\cite{Horne15:mav} extends BV with the additives.
      \item BV adds a non-commutative connective to MLL. Such a connective can be motivated by coherence spaces, or by session types.
      \item A shallow sequent calculus cannot capture BV~\cite{Tiu06:sisii}.
      \item To make sure that a proof system makes sense, we need some kind
            of Cut-elimination theorem that ensures that all proofs can be
            placed into a normal form where it is evident that it is not
            possible to derive all results.
\end{itemize}
